Carbon Nucleosynthesis

### 2023-04-07 thesis/tex/main.tex
new captions

\usepackage{setspace}

@@

% \usepackage{fancyhdr}
% \pagestyle{fancy}
% \fancyhead{}
% \fancyhead[RO,RE]{Carbon Galactic Nucleosynthesis}
\pagestyle{plain}
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}

\defcitealias{cristallo+11}{C11}
\defcitealias{cristallo+15}{C15}
\defcitealias{ventura+13}{V13}
\defcitealias{karakas10}{K10}
\defcitealias{KL16}{KL16}
\defcitealias{karakas+18}{K18}

\newcommand{\cristallo}{\citetalias{cristallo+11}+\citetalias{cristallo+15}}
\newcommand{\karakas}{\citetalias{karakas10}}
\newcommand{\kl}{\citetalias{KL16}+\citetalias{karakas+18}}
\newcommand{\ventura}{\citetalias{ventura+13}}

@@

\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm cc}}}
\newcommand{\Yct}{\ensuremath{y_{\rm C, 0}^{\rm tot}}}
\newcommand{\Yoc}{\ensuremath{y_{\rm O}^{\rm cc}}}
\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
\newcommand{\sun}{\ensuremath{\odot}}

@@

\begin{titlepage}
   \begin{center}
       \vfill
       \textbf{The Galactic Chemical Evolution of Carbon} \\
        Implications for nucleosynthesis
        \vfill
        Research Thesis
        \vfill
        Presented in partial fulfillment of the requirements for graduation \textit{with research distinction} in Astronomy and Astrophysics in the College of Arts and Sciences of The Ohio State University.
        \vfill
        by 
        \vfill
       {Danielle Alexandra Boyea}\\
       \vfill
       Department of Astronomy\\
       The Ohio State University\\
       \vfill
       April 2023
       \vfill
       Thesis Committee:\\
       David Weinberg, Advisor \\
       Jennifer Johnson \\
       Rolando Vald\'es Aguilar\\
       \vfill

   \end{center}
\end{titlepage}

% Abstract of the paper
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics. In this paper, we aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.

We find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times.

@@

Astronomy is unique among sciences in that we can determine the history of chemical elements. While stable on earth, the churning gasses and firery stars can dramatically transform elements into new materials. However, we still have much to learn about how each chemical element is made. In this work, we will hope to clarify how the chemical element carbon, the basis of life, is made in the universe.

As the universe just began to cool following the big bang, the only elements around were hydrogen, helium, and trace amounts of lithium and berylium. All other elements were formed afterwords with the help of stars. Stars of different masses, ages, and metalicities have substantially different interior stuctures. Different stars produce vastly different amounts of different chemical elements depending on their properties.

Stellar evolution, at the basis of galactical chemical evolution, predict the elemental production of different stellar processes. 
However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, opacity, and mass loss (CITE, e.g. stellar physics reviews).

Carbon and nitrogen are well studied elements as they are easy to observe (Citations...). Additionally, carbon and nitrogen are used as age indicators for giant branch stars (citations, e.g. \cite{fiorenzo+21}), and are the only light elements known to be produced significantly in Asymptotic Giant Branch Stars (AGB) (cite).

However, our theoretical understanding of the producion sources of carbon are still uncertain.

While easily visible in many stars, determining birth abundances of carbon and nitrogen are

One challenge of measuring abundances of carbon in star is that when a star becomes a RGB star, material from the CNO-processed core. Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
Additionaly, carbon is extremelt challenging to measure gas-phase abundances for because the strongest visible line is ...., e.g. carbon unreliable in GALAH, low detections.

@@

We also know that there is evidence for non-monatonic carbon yield patterns. 
pattern where carbon is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture.

Additionally, stellar models are computationally expensive, even in one dimension, so while there are grids of predictions, these are not always fine enough to make accurate chemical evolution models.

In Fig. \ref{fig:subgiants} we present a sample of APOGEE subgiants. These subgiants were chosen based on their location in the HR diagram based on criteria in \citet{jack_subgiant} replicated in Appendix \ref{sec:jack}. Because subgiants have not undergone FDU, their surface abundances are an accurate reflection of the birth abundances (CITATION).

\begin{figure}[htp]
    \includegraphics{subgiants_mgh.pdf}
    \includegraphics{subgiants_mgfe.pdf}
    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for our sample of APOGEE subgiants. On the top, we plot the high and low $\alpha$ sequences using Eq. \ref{eq:high_alpha} in blue and orange. On the bottom, we show more metal rich ([Mg/H]) stars with lighter colors.}
    \label{fig:subgiants}
\end{figure}
\chapter{Nucleosynthesis}

Nucleosynthetic predictions 
Modern theoretical nucleosynthesis provides our starting point for our models.  We focus on three primary nucleosynthetic pathways: AGB stars, CCSne, and SNeIa. Each process has unique timescales and element production which we can trace through the tools of GCE. While carbon is only known to be produced in AGB stars and CCSNe, comparing carbon to iron production (from SNeIa) adds a valuable constraint to our models and insight into the delay-time production of carbon.

@@

We focus on O and Mg as $\alpha$ elements only formed in CCSNe, and use Fe to
trace delayed enrichment from SNeIa. C and N are both formed in AGB and CCSNe.

There are two $\alpha$-elements we care about: Mg and O. Stellar observations
of magnesium are more reliable but oxygen abundances are easier to measure in
HII regions. We assume that both Mg and O are produced entirely in CCSNe with
constant, metallicity-independent yields. Thus $\text{[Mg/H]} = \text{[O/H]} =
[\alpha/\text{H}]$ in our models. (Observational validation?)

@@

As we focus on the yields of carbon, we keep yields for other elements fixed in
most models. Taken from \citet{james+21, james+22}, we let
\begin{itemize}
    \item $y_\text{Mg}^\text{CC} = 0.00185$
    \item $y_\text{Mg}^\text{Ia} = 0$
    \item $y_\text{Fe}^\text{Ia} = 0.00214$
    \item $y_\text{Fe}^\text{CC} = 0.0012$
    \item $y_\text{N}^\text{CC} = 0.00036$
    \item $\tilde{y}_\text{N}^\text{AGB}(M, Z) = 9\times 10^{-4} M \left(\frac{Z}{Z_\odot}\right)$
\end{itemize}

Also following \citet{james+21, james+22}, we take the SNeIa Delay Time distribution to be a
$t^{-1.1}$ law suggested by the observations of \citet{maoz+12}.

\section{Asymptotic giant branch carbon}\label{sec:agb}

@@

        \caption[AGB carbon yields]{The net fraction AGB carbon yield ($\tilde{y}$) plotted as a function of initial stellar mass $M$. Lighter colors represent higher values of metalicity ([M/H]). Each panel represents yields from one of our 4 AGB models: C11 \citep{cristallo+11, cristallo+15}, K10 \citep{karakas10}, V13 \citep{ventura+13,ventura+14,ventura+18}, and K16 \citep{KL16, karakas+18}.
            %C11 reports values at metallicities $Z=$ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02; K10 at $Z=$0.0001, 0.004, 0.008, 0.02; V13 at $Z=$0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04; and K16 at $Z=$0.0028, 0.007, 0.014, 0.03.
        }
            \label{fig:y_agb}
\end{figure*}

@@

    \caption[AGB yields delay time distribution]{
        The normalized delay time distribution (DTD) of AGB carbon, plotted as the net carbon enrichment $M(t)$ normalized to the total carbon enrichment mass $M_{\rm tot}$. Left: Each solid curve corresponds to an AGB yield model at solar metallicity (C11, K10, V13, or K16), and the dashed black line represents the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$). Each model has similar DTD, and most AGB enrichment occurs befor 1 Gyr. Right: each curve represents the C11 AGB model at a different metallicities. Higher metallicities cause carbon enrichment to occur earlier and for the DTD to become non-monotonic.
    }

@@

In this work, we explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
\begin{itemize}
    \item C11: \citet{cristallo+11} and \citet{cristallo+15}
    \item K10: \citet{karakas10}
    \item V13: \citet{ventura+13}
    \item K16: \citet{KL16} \citet{karakas+18}
\end{itemize}
Unless otherwise noted, C11 is the model we choose as our fiducial AGB yield.

We use IMF-Integrated yields calculated with \VICE~throughout this paper (see
section \ref{sec:vice}, \citet{james+21, james+22}). For an element X and star
with mass $M$, the stellar yield $y$ is defined as the net production of X relative 
to $M$, or
\begin{equation}
    y_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
\end{equation}
where we let $M_{\rm ejected}$ and $M_{\rm X, ejected}$ be the total ejected
stellar mass (through winds and supernovae ejecta) and the ejected mass of X,
and $Z_{0, X}$ was the birth mass fraction of element X.

More useful for GCE are Initial Mass Function (IMF) yields, where we sum up the
contributions of all stars which produce an element.
We define the IMF-integrated yield of X with: 
\begin{equation}
Y_{\rm X}^{\rm proc}(Z) = \int_{M_{\rm min}}^{M_{\rm max}} y_{\rm X}^{\rm proc}(M, Z)\ \Phi(M)  \ dM
\end{equation}
Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which we take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.

Fig. \ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model we consider. Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.

\section{CCSNe carbon}

\begin{figure}[htp]
    \centering
    \includegraphics{y_c_cc.pdf}
    \caption[CCSNe carbon yields]{Top: The net fractional IMF-weighted CCSNe yield of
        carbon, $\Ycc$ against metalicity,$\log Z/Z_\odot$, for different studies.
        The right plot instead shows the CCSNe carbon to magnisium abundance ratio, defined in Eq. \ref{eq:c_mg_cc}. The black line represents the carbon yield of the fiducial model,
    $\Ycc = 0.0029 + 0.001 (Z/Z_{\odot})$. The pink line represents the C11 AGB model.    We plot yields from \citet{WW95} as red triangles; \citep{sukhbold+16} as orange diamonds, with larger points representing models with higher explodability; \citet{NKT13} as green stars; and \citep{LC18} as blue circles. \citet{LC18} is the only model including rotation. \citet{NKT13} and \citet{WW95} also report Population III yields, plotted with arrows at the very left.}
    \label{fig:y_cc}
\end{figure}

@@

We summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. 
\begin{equation}\label{eq:c_mg_cc}
    {\rm [C/O]^{CC}} = \log_{10}\left( \frac{y_{\rm C}^{\rm CC}}{y_{\rm O}^{\rm CC}}\right) - \log_{10} \left( \frac{Z_{C, \sun }}{Z_{O, \sun }} \right)
\end{equation}
Notice how even these ratios

    \begin{itemize}
        \item Wide range in predictions, exacerbated to 1 dex range when including variance in oxygen predictions
        \item (explain) most models have a near-metallicity independent oxygen yield, so we choose the fiducial value of 0.015 despite varience in $y_O^{cc}$
        \item The fiducial value, where we choose the carbon yield from Sukhbold+16, may be above most predictions of carbon yields but is within the range of yield ratios
        \item the fiducial value would reach an equilibrium carbon yield of -0.1 without AGB stars
        \item Rotation in LC18 appears to increase metallicity dependence of carbon production (read this paper more carefully)
        \item NKT and LC agree in positive metallicity depenent yields
    \end{itemize}

@@

Chemical abundances reach an equilibrium. At least with simple enough assumptions. The new elements synthesized in stars balance against elements lost to galactic winds and locked in stellar reminants. While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, we can still use an equilibrium approximation to understand total yields.

\cite{james_dwarf}, \cite{james+22}

Following \citet{WAF17}, we assume a simple one-zone chemical evolution model. A one zone model is essentially zero-dimensional---the gas and stars are considered to be homogenously mixed, so we can represent all quantaties as scalars.

We define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star fomation rate (in M$_\odot$ yr$^{-1}$).

If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio. Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.  
We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
\begin{equation}
M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
\end{equation}

In the case that carbon
\begin{equation}
Z_c^{eq}(R) = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
\end{equation}Where
\begin{equation}
\langle y_c^{agb} \rangle = \frac{\int_0^T y_c^{agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
\end{equation}

Likewise for oxygen:
\begin{equation}
Z_O^{eq}(R) = \frac{y_O^{cc}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
\end{equation}

However, for the yield ratio, the denominator cancles with that of oxygen, so the ratio is fixed.
\begin{equation}
\frac{Z_c^{eq}}{Z_o^{eq}} = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{y_o^{cc}}
\end{equation}

For this analysis, we let $y_c^{agb}$ represent the default AGB yields from a given yield set, but add a process factor $\alpha_{agb}$ which multaplicatively increases the AGB fraction. See Table \ref{tab:alpha_agb}.

\begin{equation}
    \Ycagb \rightarrow \alpha_{agb}  \Ycagb
\end{equation}

With these definitions, we can calculate the core collapse yields of carbon as a function of metallicity:
\begin{equation}
    y_\text{C}^\text{CC} =  y_\text{O}^\text{CC} \frac{Z_\text{C,eq}}{Z_\text{O,eq}} - \alpha_{agb} \langle y_c^{agb} \rangle
\end{equation}

Rewriting in terms of the observed abundance ratio and dividing by
$y_\text{O}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the
carbon AGB yield, and the \caah mean abundance track, we can estimate the CCSNe carbon yield. Written as a relative yield:
\begin{equation}
    \frac{y_\text{C}^\text{CC}}{y_\text{O}^\text{CC}} = \frac{Z_{C, \sun}}{Z_{O, \sun}} 10^{[C/O]} - \frac{\alpha_{agb} \langle y_c^{agb} \rangle}{ y_\text{O}^\text{CC}}
\end{equation}

This equation corroberates what we have explored earlier in the paper, and provides our analytic estimates of the CCSNe carbon yields. Since the AGB term is subtracted, a negative AGB Z-dependence will correspond to a positive CC Z-dependence. And as we reduce outflows, the AGB factor increases, steepening the required slope of the carbon yields. So, while the AGB yields may agree with eachother, the uncertainties in the oxygen CC yields and outflows leads to a substantial uncertainty in the AGB fraction.

>>>>

\usepackage{setspace}
\usepackage{array}
\setlength\extrarowheight{5pt}

@@

% \usepackage{fancyhdr}
% \pagestyle{fancy}
% \fancyhead{}
% \fancyhead[RO,RE]{Carbon Galactic Nucleosynthesis}
\pagestyle{plain}
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}
\counterwithout{equation}{chapter}

\defcitealias{cristallo+11}{C11}
\defcitealias{cristallo+15}{C15}
\defcitealias{ventura+13}{V13}
\defcitealias{karakas10}{K10}
\defcitealias{KL16}{KL16}
\defcitealias{karakas+18}{K18}
\defcitealias{james+21}{J21}

\newcommand{\JJ}{\citetalias{james+21}}
\newcommand{\cristallo}{\citetalias{cristallo+11}+\citetalias{cristallo+15}}
\newcommand{\karakas}{\citetalias{karakas10}}
\newcommand{\kl}{\citetalias{KL16}+\citetalias{karakas+18}}
\newcommand{\ventura}{\citetalias{ventura+13}}

@@

\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
\newcommand{\Yct}{\ensuremath{y_{\rm C, 0}^{\rm tot}}}
\newcommand{\Yoc}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
\newcommand{\sun}{\ensuremath{\odot}}

\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
\newcommand{\possesivecite}[1]{\citeauthor{#1}'s \citeyearpar{#1}}

\setcitestyle{aysep={}} 
\setcitestyle{notesep={; }}

@@

\begin{titlepage}
   \begin{center}
       \vfill
       \textbf{The Galactic Chemical Evolution of Carbon} \\
       [3\baselineskip]
        Undergraduate Research Thesis\\
       [3\baselineskip]
    Presented in partial fulfillment of the requirements for graduation \textit{with research distinction in Astronomy and Astrophysics} in the College of Arts and Sciences of The Ohio State University \\
       [3\baselineskip]
        by \\
       {Daniel Alexander Boyea}\\
       [3\baselineskip]
       The Ohio State University\\
       April 2023\\
       [3\baselineskip]
       Project Advisor: David Weinberg, Department of Astronomy
       % Rolando Vald\'es Aguilar\\
       \vfill
   \end{center}
\end{titlepage}

% Abstract of the paper
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics. In this paper, I aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.

I find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times.

@@

Galactic chemical evolution (GCE) aims to understand the chemical and star formation history of galaxies. At the core of GCE models are stellar yields---the amount of each chemical element stars produce (or destroy). Different chemical elements are produced in different sites, so stars leave traces of the Galaxy's chemical history. Through \textit{Galactic Archeology}, I can reconstruct the history of our galaxy by investigating the clues left in the remains---stars from the early universe \citep{Weinberg+22, emily+19}.

I aim to understand the GCE of carbon, where the element is produced and how the abundances of this element evolve over time. Why stuy carbon? Carbon is unique nucleosynthetically, one of few light elements (along with nitrogen) which are produced in Asymptotic Giant Branch (AGB) stars \citep[for example,][]{jennifer19, KL14}. Carbon and nitrogen are well studied elements as they are easy to observe in stellar spectra, even at the lowest metallicities \citep{FN15} SOMETHING ELSE?. Additionally, carbon and nitrogen are used as age indicators in red giant branch stars \citep[e.g.][]{martig16, MG15, fiorenzo+21}.
While we know carbon is produced in AGB stars and core collapse supernovae (CCSNe), we still have limited understanding of the importaince and metallicity-dependence of each process.

We also know that there is evidence for non-monatonic carbon yield patterns. 
pattern where carbon is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture. \citep{FN15,cooke+17,berg+19}.

Stellar evolution models predict stellary yields, playing a crucial role in GCE.  However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, rotational mixing, opacity, and mass loss CITATIONS. Changes in opacity, rotation, reaction rates, and explodability can substantially affect carbon yields \citep{KL14,V13, LC18, emily+21}.

GCE models typically use unmodified nucleosythetic predictions and attempt to create models matching observaions by varying star formation history and other parameters. I instead use the observations as a constraint, determining which yield assuptions are consistant with galactic abundance trends.

While there are many stellar measurments of carbon, accurately determining the birth abundance is more challenging. For example, when a star becomes a RGB star, material from the CNO-processed core \citep{fiorenzo+21,KL14}. Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.  Additionaly, carbon is faint in HII regions and determining gas-phase abundances is challenging \citet{skillman+20}.
Other surveys, such as GALAH, have unreliable carbon measurments with low detection rates \citep{emily+19}.

@@

In Fig. \ref{fig:subgiants}, I present a sample of APOGEE subgiants. These subgiants were chosen based on their location in the HR diagram based on the criteria in \citet{jack_subgiant} also replicated in Appendix \ref{sec:jack}. Because subgiants have not undergone FDU, their surface abundances are an accurate reflection of the birth abundances (CITATION).

\begin{figure}[htp]
    \includegraphics{subgiants_mgh.pdf}
    \includegraphics{subgiants_mgfe.pdf}
    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for our sample of APOGEE subgiants. On the top, I plot high-$\alpha$ stars in blue and low-$\alpha$ stars in orange using the seperation defined in Equation \ref{eq:high_alpha}. On the bottom, I colorcode stars according to their [Mg/H] abundance.}
    \label{fig:subgiants}
\end{figure}
\chapter{Nucleosynthesis}

Modern theoretical nucleosynthesis provides the starting point for our models.  I focus on three primary nucleosynthetic pathways: AGB stars, CCSne, and SNeIa. Each process has unique timescales and element production which I can trace through the tools of GCE. While carbon is only known to be produced in AGB stars and CCSNe, comparing carbon to iron production (from SNeIa) adds a valuable constraint to our models and insight into the delay-time production of carbon.

@@

I focus on O and Mg as $\alpha$ elements only formed in CCSNe, and use Fe to
trace delayed enrichment from SNeIa. C and N are both formed in AGB and CCSNe.

There are two $\alpha$-elements I care about: Mg and O. Stellar observations
of magnesium are more reliable but oxygen abundances are easier to measure in
HII regions. I assume that both Mg and O are produced entirely in CCSNe with
constant, metallicity-independent yields. Thus $\text{[Mg/H]} = \text{[O/H]} =
[\alpha/\text{H}]$ in our models. (Observational validation?)

@@

To calculate the net initial mass function (IMF)-weighted yields, I use the \citet{james+21} model (hereafter \JJ) with the Versatile Integrator for Chemical Evolution code (\VICE).
As stellar evolution models predict per-star yields for stars of each mass, we need to integrate over the IMF to determine the total yields in terms of star formation.

As the focus of this work is on carbon yields, I keep all other yields fixed. The yields I use are based on \citet{james+21, james+22}.

Also following \citet{james+21, james+22}, I take the SNeIa Delay Time distribution to be a
$t^{-1.1}$ law suggested by the observations of \citet{maoz+12}.

\begin{table}
	\centering
    \caption[Fiducial Model]{Yields for the fiducial model}
	\label{tab:fiducial_mod}
	\begin{tabular}{l l l l}
		\hline
        Element & $\Ycc$ & $\tilde{y}^{\rm AGB}$ & $y^{\rm SNe Ia}$ \\
		\hline
        C & $0.0028 + 0.001(Z/Z_\odot)$ & $2.9\times{\rm C11}$ &  0 \\
        Mg & 0.00185 & 0 & 0 \\
        Fe & 0.0012 & 0 & 0.00214 \\
        N & 0.00072 & $9\times10^{-4}(Z/Z_\odot)M$ & 0\\
		\hline
	\end{tabular}
\end{table}

\section{Asymptotic giant branch stars}\label{sec:agb}

In this work, I explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
\begin{itemize}
    \item C11: \citet{cristallo+11} and \citet{cristallo+15}
    \item K10: \citet{karakas10}
    \item V13: \citet{ventura+13}
    \item K16: \citet{KL16} \citet{karakas+18}
\end{itemize}
Unless otherwise noted, C11 is the model I choose as our fiducial AGB yield.

I use IMF-Integrated yields calculated with \VICE~throughout this paper (see
section \ref{sec:vice}, \citet{james+21, james+22}). For an element X and star
with mass $M$, the stellar yield $y$ is defined as the net production of X relative 
to $M$, or
\begin{equation}
    y_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
\end{equation}
where I let $M_{\rm ejected}$ and $M_{\rm X, ejected}$ be the total ejected
stellar mass (through winds and supernovae ejecta) and the ejected mass of X,
and $Z_{0, X}$ was the birth mass fraction of element X.

More useful for GCE are Initial Mass Function (IMF) yields, where I sum up the
contributions of all stars which produce an element.
I define the IMF-integrated yield of X with: 
\begin{equation}
Y_{\rm X}^{\rm proc}(Z) = \int_{M_{\rm min}}^{M_{\rm max}} y_{\rm X}^{\rm proc}(M, Z)\ \Phi(M)  \ dM
\end{equation}
Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.

Fig. \ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model I consider. Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.

@@

        \caption[AGB carbon yields]{The net fractional AGB carbon yield ($\tilde{y}$) plotted as a function of initial stellar mass $M$. Metallicity is colorcoded according to the colorbar. I plot $\tilde{y}=0$ for reference. Each panel represents yields from one of four AGB models: C11 \citep{cristallo+11, cristallo+15}, K10 \citep{karakas10}, V13 \citep{ventura+13,ventura+14,ventura+18}, and K16 \citep{KL16, karakas+18}.
            %C11 reports values at metallicities $Z=$ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02; K10 at $Z=$0.0001, 0.004, 0.008, 0.02; V13 at $Z=$0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04; and K16 at $Z=$0.0028, 0.007, 0.014, 0.03.
        }
            \label{fig:y_agb}
\end{figure*}

@@

    \caption[AGB yields delay time distribution]{
        Carbon production by AGB stars as a function of SSP age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr. Left: The four AGB yield models from liturature  at solar metallicity (C11, K10, V13, or K16). The delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison. Each model has a similarly shaped DTD, and most AGB enrichment occurs before 1 Gyr. Right: The C11 AGB model at different metallicities. With increasing metallicity, carbon enrichment occurs earlier, and the DTD eventually becomes non-monotonic.
    }

@@

\section{Core collapse supernovae}

@@

I summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. 
\begin{equation}\label{eq:c_mg_cc}
    {\rm [C/O]^{CC}} = \log_{10}\left( \frac{y_{\rm C}^{\rm CC}}{y_{\rm O}^{\rm CC}}\right) - \log_{10} \left( \frac{Z_{C, \sun }}{Z_{O, \sun }} \right)
\end{equation}
Notice how even these ratios

    \begin{itemize}
        \item Wide range in predictions, exacerbated to 1 dex range when including variance in oxygen predictions
        \item (explain) most models have a near-metallicity independent oxygen yield, so I choose the fiducial value of 0.015 despite varience in $y_O^{cc}$
        \item The fiducial value, where I choose the carbon yield from Sukhbold+16, may be above most predictions of carbon yields but is within the range of yield ratios
        \item the fiducial value would reach an equilibrium carbon yield of -0.1 without AGB stars
        \item Rotation in LC18 appears to increase metallicity dependence of carbon production (read this paper more carefully)
        \item NKT and LC agree in positive metallicity depenent yields
    \end{itemize}

\begin{figure}[htp]
    \centering
    \includegraphics{y_c_cc.pdf}
    \caption[CCSNe carbon yields]{
        Carbon yields from massive stars.
        Top: The net fractional IMF-weighted CCSNe yield of carbon (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function) as a function of metallicity.
        Bottom: The CCSNe carbon to magnisium abundance ratio, defined in Equasion \ref{eq:c_mg_cc}. The black line represents the carbon yield of the fiducial model,
    $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. 
    \citet[red triangles]{WW95}, \citet[orange squares and diamonds]{sukhbold+16}, 
    \citet[green stars]{NKT13}, and \citet[blue circles]{LC18}. \citet{sukhbold+16} report yields for different black hole landscales, while \citet{LC18} provide yields at different roational velocities.
The pink line represents the C11 AGB model.
}
    \label{fig:y_cc}
\end{figure}

@@

Chemical abundances reach an equilibrium. At least with simple enough assumptions. The new elements synthesized in stars balance against elements lost to galactic winds and locked in stellar reminants. While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, I can still use an equilibrium approximation to understand total yields \citep[e.g.][]{james_dwarf,james+22,WAF17}.

Following the formalism of \citet{WAF17}, I assume a simple one-zone chemical evolution model. The gas and stars are considered to be homogenously and instantaneusly mixed, so I can represent all quantaties as scalars.
I define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star fomation rate (in M$_\odot$ yr$^{-1}$). $\eta$ is the mass loading factor, $\eta=\dot{M}_{\rm outflow}/\dot{M}_\star$, representing the strength of outflows. $r$ is the recycling fraction, i.e. the net fraction of new star formation which will be returned to the ISM.

Given the total IMF-weighted yield of magnesium, $y_{\rm Mg}$, I can write the change in the ISM mass of magnesium, $\dot{M}_{\rm Mg}$ as the sum of newly produced elements, elements lost inside stellar remanents, and elements lost to galactic outflows.
\begin{equation}
    \frac{d{M}_{\rm Mg}}{dt} = \dot{M}_{\rm Mg,~new} - \dot{M}_{\rm Mg~reminants} - \dot{M}_{\rm Mg,~outflows}
\end{equation}
The newly produced mass can be written in terms of the yield, $\dot{M}_{X,\rm~new}=y_X\dot{M}_\star$. In terms of the return mass fraction of stars $r$, the mass lost to reminants is $Z_X (1-r)\dot{M}_\star$.  And, the outflows deplete a mass $Z_X \eta\dot{M}_\star$. Substituting, 
\begin{equation}
    \frac{d{M}_{X}}{dt} = y_{X} \dot{M}_\star - (1 + \eta - r) Z_{X} \dot{M}_\star
\end{equation}
\citep{WAF17}.
Assuming an exponentially declining star formation history, $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, this equation can be solved analytically. 
To find equilibrium, set $\dot{M}_X=0$, and now
\begin{equation}\label{eq:z_eq}
    Z_{\rm Mg}^{\rm eq}(R) = \frac{y_{\rm Mg}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
\end{equation}
For constant star formation, $\tau_\star/\tau_{\rm sfh} \rightarrow 0$

While Equation \ref{eq:z_eq} can be applied to CCSNe carbon, the delayed time contribution of AGB carbon can complicate the result. Instead, using an effective or DTD-integrated yield, $\langle \Ycagb \rangle$
\begin{equation}
    \langle \Ycagb\rangle = \frac{\int_0^T \tilde{y}_{\rm C}^{\rm agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
\end{equation}
So, for carbon, Equation \ref{eq:z_eq} becomes
\begin{equation}
    Z_{\rm C}^{\rm eq}(R) = \frac{\Ycc + \langle\Ycagb\rangle}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
\end{equation}
Taking the ratio of $Z_{\rm C}$ and $Z_{\rm Mg}$, 
\begin{equation}\label{eq:z_co}
    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \langle \Ycagb \rangle }{\Yoc}
\end{equation}

With these definitions, I can calculate the core collapse yields of carbon as a function of metallicity:
\begin{equation}
    y_\text{C}^\text{CC} =  y_\text{Mg}^\text{CC} \frac{Z_\text{C,~eq}}{Z_\text{Mg,~eq}} - \langle y_c^{agb} \rangle
\end{equation}

Rewriting in terms of the observed abundance ratio and dividing by
$y_\text{Mg}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the
carbon AGB yield, and the \caah mean abundance track, I can estimate the CCSNe carbon yield. Written as a relative yield:
\begin{equation}
    \frac{\Ycc}{\Yoc} = \frac{Z_{\text{C},~\sun}}{Z_{\text{Mg},~\sun}} 10^{[C/Mg]} - \frac{\langle \Ycagb \rangle}{\Yoc}
\end{equation}
